---
title: "Statistical Inference Project"
author: "arturop@gmail.com"
output: html_document
---
## Overview
In this report I look at the ToothGrowth data from the R datasets package and, after some exploratory analysis, try to summarise what I see and compare growth by supp and dose based on hypothesis tests, laying out the assumptions I based my results on.

### Basic Inferential Data Analysis

The ToothGrowth dataset observes the response of odontoblasts (cells responsible for tooth growth) on 60 guinea pigs. Animals are split in two groups according to the supplement they are given. Each animal then receives the same dose of the same component each day for an unspecified period.

The following scatterplot shows the tooth growth by supplement and dose

```{r}
data(ToothGrowth)
coplot(len ~ dose | supp, data = ToothGrowth, panel = panel.smooth,
       xlab = "ToothGrowth data: length vs dose, given type of supplement")
```

I am going to try to establish if, from a tooth growth perspective, it is preferable to administer the VC supplement over the OJ supplement for each type of dosage. Our null hypothesis will hence be that for any given dosage OJ produces the highest growth. As the number of observations is small, I will use a t-distribution.

For a 0.5 dose we have:

```{r}
t.test(len ~ supp, data = ToothGrowth[ToothGrowth$dose == 0.5,], paired = FALSE, var.equal = FALSE)
```

For a 1.0 dose we have:

```{r}
t.test(len ~ supp, data = ToothGrowth[ToothGrowth$dose == 1,], paired = FALSE, var.equal = FALSE)
```

For a 2.0 dose we have:

```{r}
t.test(len ~ supp, data = ToothGrowth[ToothGrowth$dose == 2,], paired = FALSE, var.equal = FALSE)
```

We can see that in neither of the three cases we are able to reject the null hypothesis as the t stat for all of them falls squarely into the respective confidence intervals (at 95% level).

Conclusion we can't establish that the VC supplementation is superior to the OJ supplementation.